### 2014-02-21 tex/pseudo-code.tex
Added
Made function
Added refined formating on function
Added new
added more detail to the equals (references true) rule

>>>>

The function $\mathbb{VS}(L,R,r,f)$ constructs the value-set given a
heap, reference, and desired field such that
$(l^\prime\ \phi^\prime\wedge\phi) \in \mathbb{VS}(L,R,r,f)$ if and
only if
\[
\begin{array}{l}
  \exists (l\ \phi) \in L(r) ( \\
  \ \ \ \ \ \ \ \ \ \exists r^\prime \in R(l,f) ( \\
  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists (l^\prime\ \phi^\prime) \in L(r^\prime) (\mathbb{S}(\phi\wedge\phi^\prime))))
\end{array}
\]
where $\mathbb{S}(\phi)$ returns true if $\phi$ is satisfiable.

The function $\mathbb{CP}(L,r,\phi^\prime)$ constructs the location, constraint
pair $(l\ \phi\wedge\phi^\prime)$ such that $(l\ \phi\wedge\phi^\prime)\in\mathbb{CP}(L,r,\phi^\prime)$ if and only if $\exists (l\ \phi)\in L(r)\wedge\mathbb{S}(\phi\wedge\phi^\prime)$
